### 2008-12-21 talk/ecoop2009/intro.tex
fix xxx

Most JIT compilers for dynamic languages around (such as
IronPython \footnote{http://www.codeplex.com/IronPython},
Jython \footnote{http://www.jython.org/} or
JRuby \footnote{http://jruby.codehaus.org/}) compile code at the method
granularity.  If on the one hand they can exploit some of the knowledge
gathered at runtime (e.g. the types of method parameters), on the other hand
they can do little to optimize most of the operations inside, because few
assumptions can be made about the global state of the program.

>>>>

Most JIT compilers for dynamic languages around (such as
IronPython\footnote{http://www.codeplex.com/IronPython},
Jython\footnote{http://www.jython.org/} or
JRuby\footnote{http://jruby.codehaus.org/}) compile code at the method
granularity.  If on the one hand they can exploit some of the knowledge
gathered at runtime (e.g. the types of method parameters), on the other hand
they can do little to optimize most of the operations inside, because few
assumptions can be made about the global state of the program.

### 2008-12-21 talk/ecoop2009/jitgen.tex
some minore changes
fix xxx

Traditional JIT compilers are hard to write, time consuming, hard to evolve,
etc. etc.

>>>>

Traditional JIT compilers are hard to write, time consuming and hard to
evolve.  On the other hand, interpreters are easy both to write and maintain,
but they are usually slow.  By automatically generating a JIT compiler out of
an interpreter, we take the best of both worlds.
